---
title: "Homework 2"
author: "Maxwell Miller-Golub & Kevwe Okogu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 2)

library(tidyverse)
```

## Problem 1:

``` {r 613_hw2_1.tribble}

problem_1_dt <- tribble( 
  ~x, ~y,    ~w,    ~z,
210,   300,   220,   180,
102,   100,   119,   187,
176,   175,   188,   173,
87,    95,   91,     94,
202,   210,  234,    218,
110,   122,  131,    128)

```

### 1_a: Use and show a map function to find the “mean” of each column of the dt data table 

``` {r 613_hw2_1.a}
map_dbl(problem_1_dt, mean)
```

### 1_b: Use and show a map function to find the “standard deviation” of each column of the dt data table.

``` {r 613_hw2_1.b}
map_dbl(problem_1_dt, sd)
```

### 1_c: Use and show a map function that will calculate the “square root” of each value of each column of the data table dt.

``` {r 613_hw2_1.c}
map(problem_1_dt, sqrt)
```

### 1_d: Use R code to find the “mean”, “max”, “1st Quartile”, “3rd Quartile”, “Median”, and “Min” for each column of the dt data table. (Hint: You do not have to use a map function)

``` {r 613_hw2_1.d}
sapply(problem_1_dt, summary)
```

## Problem 2: Write a function that uses a for loop that, for each iteration, randomly draws 5 observations from an exponential distribution with “rate” parameter 1 (use rexp()) and calculates its “mean”. It should do this 10,000 times. Choose an appropriate plot to plot the distribution of “means”.

``` {r 613_hw2_2}
Ten_Thousand_Means <- c()
for (i in 1:10000){
  FiveObservations <- rexp(5, rate = 1)
  Ten_Thousand_Means <- append(Ten_Thousand_Means, mean(FiveObservations))
}

hist(Ten_Thousand_Means)
```

### 2_a: Repeat part 1 by using a map_*() function. 

``` {r 613_hw2_2a}
Ten_Thousand_Lists <- c()
for (i in 1:10000){
  FiveObservations <- list(rexp(5, rate = 1))
  Ten_Thousand_Lists <- append(Ten_Thousand_Lists, FiveObservations)
}

MappedMeans <- map_dbl(Ten_Thousand_Lists, mean)

hist(MappedMeans)
```

### 2_b: Repeat part 1 by using the replicate() function.

``` {r 613_hw2_2b}
replicate_ten_thousand <- replicate(10000, mean(rexp(5, 1)))

hist(replicate_ten_thousand)
```

### 2_c: Use a another for loop that will print out plots for sample sizes of 5, 10, and 20 observations (instead of just 5).

``` {r 613_hw2_2c}
Ten_Thousand_Five <- c()
Ten_Thousand_Ten <- c()
Ten_Thousand_Twenty <- c()

for (i in 1:10000){
  FiveObservations <- mean(rexp(5, rate = 1))
  TenObservations <- mean(rexp(10, rate = 1))
  TwentyObservations <- mean(rexp(20, rate = 1))
  
  Ten_Thousand_Five <- append(Ten_Thousand_Five, mean(FiveObservations))
  Ten_Thousand_Ten <- append(Ten_Thousand_Ten, mean(TenObservations))
  Ten_Thousand_Twenty <- append(Ten_Thousand_Twenty, mean(TwentyObservations))
}

hist(Ten_Thousand_Five)
hist(Ten_Thousand_Ten)
hist(Ten_Thousand_Twenty)
```

## Problem 3: Use and show R coding to calculate the “standard deviation” for each variable of the data table mtcars using the “Special For Loop Method”.

Note: There are two methods. Please see a quick explanation for both methods in below:

Method 1:
``` {r 613_hw2_3_demo1}        
multi_return <- function() {
  my_list <- list("color" = "red", "size" = 20, "shape" = "round")
  return(my_list)
}
a <- multi_return()
a$color
  
a<- multi_return()
a$shape

a<- multi_return()
a$size

```

Method 2. The “Special For Loop Method”

``` {r 613_hw2_3_demo2} 
# 1. output (use appropriate data frame instead of df)
# 2. sequence
# 3. body

output <- vector("double", ncol(df))

for (i in seq_along(df)) {
  output[[i]] <- median(df[[i]])
}

output
```