---
title: "Homework 2"
author: "Maxwell Miller-Golub & Kevwe Okogu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 2)

library(tidyverse)
```

## Problem 1:

``` {r 613_hw2_1.tribble}

problem_1_dt <- tribble( 
  ~x, ~y,    ~w,    ~z,
210,   300,   220,   180,
102,   100,   119,   187,
176,   175,   188,   173,
87,    95,   91,     94,
202,   210,  234,    218,
110,   122,  131,    128)

```

### 1_a: Use and show a map function to find the “mean” of each column of the dt data table 

``` {r 613_hw2_1.a}
map_dbl(problem_1_dt, mean)
```

### 1_b: Use and show a map function to find the “standard deviation” of each column of the dt data table.

``` {r 613_hw2_1.b}
map_dbl(problem_1_dt, sd)
```

### 1_c: Use and show a map function that will calculate the “square root” of each value of each column of the data table dt.

``` {r 613_hw2_1.c}
map(problem_1_dt, sqrt)
```

### 1_d: Use R code to find the “mean”, “max”, “1st Quartile”, “3rd Quartile”, “Median”, and “Min” for each column of the dt data table. (Hint: You do not have to use a map function)

``` {r 613_hw2_1.d}
sapply(problem_1_dt, summary)
```

## Problem 2: Write a function that uses a for loop that, for each iteration, randomly draws 5 observations from an exponential distribution with “rate” parameter 1 (use rexp()) and calculates its “mean”. It should do this 10,000 times. Choose an appropriate plot to plot the distribution of “means”.

``` {r 613_hw2_2}
Ten_Thousand_Means <- c()
for (i in 1:10000){
  FiveObservations <- rexp(5, rate = 1)
  Ten_Thousand_Means <- append(Ten_Thousand_Means, mean(FiveObservations))
}

hist(Ten_Thousand_Means)
```

### 2_a: Repeat part 1 by using a map_*() function. 

``` {r 613_hw2_2a}
Ten_Thousand_Lists <- c()
for (i in 1:10000){
  FiveObservations <- list(rexp(5, rate = 1))
  Ten_Thousand_Lists <- append(Ten_Thousand_Lists, FiveObservations)
}

MappedMeans <- map_dbl(Ten_Thousand_Lists, mean)

hist(MappedMeans)
```

### 2_b: Repeat part 1 by using the replicate() function.

``` {r 613_hw2_2b}
replicate_ten_thousand <- replicate(10000, mean(rexp(5, 1)))

hist(replicate_ten_thousand)
```

### 2_c: Use a another for loop that will print out plots for sample sizes of 5, 10, and 20 observations (instead of just 5).

``` {r 613_hw2_2c}
Ten_Thousand_Five <- c()
Ten_Thousand_Ten <- c()
Ten_Thousand_Twenty <- c()

for (i in 1:10000){
  FiveObservations <- mean(rexp(5, rate = 1))
  TenObservations <- mean(rexp(10, rate = 1))
  TwentyObservations <- mean(rexp(20, rate = 1))
  
  Ten_Thousand_Five <- append(Ten_Thousand_Five, mean(FiveObservations))
  Ten_Thousand_Ten <- append(Ten_Thousand_Ten, mean(TenObservations))
  Ten_Thousand_Twenty <- append(Ten_Thousand_Twenty, mean(TwentyObservations))
}

par(mfrow = c(1, 3))  # Set up the plotting window for three plots side by side

hist(Ten_Thousand_Five, main = "Sample Size = 5", xlab = "Means", col = "lightblue")
hist(Ten_Thousand_Ten, main = "Sample Size = 10", xlab = "Means", col = "lightgreen")
hist(Ten_Thousand_Twenty, main = "Sample Size = 20", xlab = "Means", col = "lightcoral")

```

## Problem 3: Use and show R coding to calculate the “standard deviation” for each variable of the data table mtcars using the “Special For Loop Method”.

```{r 613_hw_3}
#Loading the mtcars dataset
data(mtcars)

#Now creating an empty vector that will store the standard deviations.
output <- vector("double", ncol(mtcars))


#This For Loop can calculate the standard deviation for each column.
for (i in seq_along(mtcars)) {
  output[i] <- sd(mtcars[[i]])
}

#To ensure that the 'mtcars' column names are included in the results.
names(output) <- colnames(mtcars)

# Display the standard deviations
output
```
