---
title: "Homework 2"
author: "Maxwell Miller-Golub & Kevwe Okogu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 2)

library(tidyverse)
```

## Problem 1:

``` {r 613_hw2_1.tribble}

problem_1_dt <- tribble( 
  ~x, ~y,    ~w,    ~z,
210,   300,   220,   180,
102,   100,   119,   187,
176,   175,   188,   173,
87,    95,   91,     94,
202,   210,  234,    218,
110,   122,  131,    128)

```

### 1_a: Use and show a map function to find the “mean” of each column of the dt data table 

``` {r 613_hw2_1.a}
map_dbl(problem_1_dt, mean)
```

### 1_b: Use and show a map function to find the “standard deviation” of each column of the dt data table.

``` {r 613_hw2_1.b}
map_dbl(problem_1_dt, sd)
```

### 1_c: Use and show a map function that will calculate the “square root” of each value of each column of the data table dt.

``` {r 613_hw2_1.c}
map(problem_1_dt, sqrt)
```

### 1_d: Use R code to find the “mean”, “max”, “1st Quartile”, “3rd Quartile”, “Median”, and “Min” for each column of the dt data table. (Hint: You do not have to use a map function)

``` {r 613_hw2_1.d}
sapply(problem_1_dt, summary)
```
