---
title: "SQL_Class_Practice"
author: "Maxwell Miller-Golub"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("duckdb")
library(DBI)
library(duckdb)
con <- dbConnect(duckdb(dbdir = "flights.duckdb", read_only = TRUE))
```

### Practice 1: Select Flights from a Specific Carrier
Write a SQL query to find all flights from the carrier "United Air Lines Inc.".

```{sql, connection=con}
SELECT *
FROM flights
WHERE carrier = 'UA';
```

### Practice 2: Count the Number of Flights for Each Carrier
Write a SQL query to count the total number of flights for each carrier.

```{sql, connection=con}
SELECT "carrier", count(carrier)
FROM flights
GROUP BY "carrier";
```

### Practice 3: Find the Flights with the Longest Distance
Write a SQL query to find the 10 longest flights based on the distance column.

```{sql, connection=con}
SELECT "ANY_VALUE"(carrier), "distance"
FROM flights
GROUP BY "distance"
ORDER BY "distance" DESC
LIMIT 10;
```

### Practice 4: Calculate Average Arrival Delay for Each Carrier
Write a SQL query to calculate the average arrival delay (arr_delay) for each carrier, showing only those with a non-null delay.

```{sql, connection=con}
SELECT "carrier", AVG("arr_delay")
FROM flights
WHERE "arr_delay" IS NOT NULL
GROUP BY "carrier";
```

### Practice 5: Find Flights Departing from JFK to LAX
Write a SQL query to find all flights departing from JFK airport to LAX airport.

```{sql, connection=con}
SELECT *
FROM flights
WHERE "origin" = 'JFK' AND "dest" = 'LAX';
```

### Practice 6: Calculate the Total Number of Flights Each Month
Write a SQL query to count the total number of flights for each month.

```{sql, connection=con}
SELECT "month", count(flight)
FROM flights
GROUP BY "month";
```

### Practice 7: Find Flights with Departure Delays Greater than 2 Hours
Write a SQL query to find all flights that had a departure delay of more than 120 minutes.

```{sql, connection=con}
SELECT "flight", "dep_delay"
FROM flights
WHERE "dep_delay" > 120;
```

### Practice 8: Find the Number of Flights per Day
Write a SQL query to count the number of flights for each day (use year, month, and day columns).

```{sql, connection=con}
SELECT CONCAT("month",'/',"day",'/',"year") AS DATE, COUNT("flight")
FROM flights
GROUP BY DATE;
```

### Practice 9: Find Flights That Arrived Early
Write a SQL query to find all flights that arrived early (i.e., arr_delay is negative).

```{sql, connection=con}
SELECT "flight", "arr_delay"
FROM flights
WHERE "arr_delay" < 0;
```

### Practice 10: Find the Average Air Time per Carrier
Write a SQL query to find the average air time for each carrier.

```{sql, connection=con}
SELECT "carrier", AVG("air_time")
FROM flights
GROUP BY "carrier";
```

```{r}
DBI::dbDisconnect(con, shutdown = TRUE)
```